---
title: "Reading&Writing"
date: "02/19/2015"
output: html_document
---

-1 

0. scan
what would you do if...

```{r}
scan()
scan(what = "character")
```
BUT IT'S NOT REPRODUCIBLE

0.1 RKward

https://rkward.kde.org/
$ apt-get install rkward

1. Reading
1.1. Reading tables (decimal point etc) + usual problems + 

No matter whether found on the Net or in a local file.

```{r}
#download.file("https://raw.githubusercontent.com/drozdovapb/r-15-data/master/Table01.csv")
#download.file("https://raw.githubusercontent.com/drozdovapb/r-15-data/master/Table01.csv", 
#              destfile='Table01.csv')
download.file("https://raw.githubusercontent.com/drozdovapb/r-15-data/master/lab02/Table01.csv", destfile='Table01.csv', method='curl')

download.file("https://raw.githubusercontent.com/drozdovapb/r-15-data/master/lab02/Tables.zip", 
              destfile="Tables.zip", method='curl')
unzip('Tables.zip')
```

+ reading data from the net: curl etc

Problem: never tells the file doesn't exist
like here:

```{r}
download.file("https://raw.githubusercontent.com/drozdovapb/r-15-data/master/Table02.csv2", 
              destfile='Table02.csv2', method='curl')
download.file("https://raw.githubusercontent.com/drozdovapb/r-15-data/master/Table03.txt", 
              destfile='Table03.txt', method='curl')

```



read.table
read.csv; read.csv2; read.delim

```{r}

table01 <- read.table('Table01.csv') ###Only 1 column
str(table01)

table01 <- read.table('Table01.csv', sep=',') #ok but why factors?
str(table01)
table01 <- read.table('Table01.csv', sep=',', head = T) #ok but why factors in the 1st column?
str(table01)

table01 <- read.table('Table01.csv', sep=',', head = T, stringsAsFactors = F) #ok but why factors?

#OR
table01 <- read.csv('Table01.csv') #the same problem with factors
str(table01)
```

DELIMITERS!!!!
, vs .
And how to change 

typical errors


```{r}
#install.packages('xlsx')
library(xlsx)
read.xlsx('Table04.xlsx', sheetIndex = 1)
```
xls: gdata; xlsReadWrite; xlsx
see http://www.milanor.net/blog/?p=779



what should R consider as NA

comment.char
skip

```{r}

readLines('Table05.txt')
read.table('Table05.txt')


#read.table('Table06.txt')
readLines('Table06.txt')
```


data.table (fread)


```{r}
#install.packages('data.table')
library(data.table)

system.time(read.table('Table01.csv'))
system.time(fread('Table01.csv'))

download.file("https://raw.githubusercontent.com/drozdovapb/r-15-data/master/lab02/Table13.txt", 
              destfile = 'Table13.txt', method='curl')


system.time(read.table('Table13.txt'))
system.time(fread('Table13.txt'))

```

1.2. Reading images
the jpeg package

```{r}
#install.packages('jpeg')
library(jpeg)
myjpeg <- download.file("http://www.pmglobalpm.com/wp-content/uploads/2013/02/compliance-150x150.jpg", destfile = 'myjpeg.jpeg', method='curl')
myimg <- readJPEG('myjpeg.jpeg')
    
greencat <- myimg[,,2]
image(greencat)
image(t(greencat))
image(greencat[nrow(greencat):1,])
image(t(greencat[nrow(greencat):1,]))
```

Hometask:
debug these tables ;)

download zip!!! +1 point
1. csv with tab separator +1
(2. csv2 with ; separators )
(3. cvs with commas as decimal separator) +2
(4. additional header with # (or many headers) #skip) +2
5. StringsAsFactors


http://www.r-bloggers.com/using-r-common-errors-in-table-import/

xlsx:
http://tuxette.nathalievilla.org/?p=1380&lang=en