---
title: "Fig 4 Hoechst experiment"
author: "Polina Drozdova"
date: "2022-10-18"
output: html_document
---

## Introduction. Loading packages.

```{r, include=TRUE}
check_install_load <- function(packagename) {
  if (!(packagename %in% installed.packages()))
    install.packages(packagename)
  library(packagename, character.only = TRUE)
  }

check_install_load("openxlsx")
check_install_load("ggplot2")
check_install_load("ggsignif")
check_install_load("dunn.test")
check_install_load("magrittr")
check_install_load("multipanelfigure")
```

## Loading data & necessary adjustments

```{r}
dat <- read.xlsx("Data/Fig4_exp_data_all.xlsx")

dat$Inhibitor <- paste(dat$`Inhibitor,.type`, dat$`Inhibitor,.concentration`)
dat$Inhibitor <- gsub("without inhibitor NA", "Control (no inhibitor)", dat$Inhibitor)

dat$cell.type <- factor(dat$cell.type, levels = c("mScarlet", "abcb1", "abcb1-mScarlet"))
```


## Plot all the data (3 cell lines x controls / inhibitors)

```{r plot, echo=FALSE}
pall <- 
ggplot(dat, aes(Inhibitor, log10(RawintDen_H+1), col = cell.type, fill = Inhibitor)) + 
  geom_boxplot() + #geom_jitter(width = .1) +
  #  geom_signif(comparisons = list(c("without inhibitor NA", "CyclosporinA  6.25 uM", "CyclosporinA  25 uM"))) + 
  facet_wrap(~ cell.type) +
#  geom_hline(yintercept = bkgnd, linetype = "dotted") + 
  ylab("log fluorescence intensity") + 
  theme_bw() + theme(axis.text.x = element_text(angle = 90)) + 
  scale_color_manual(values = c("grey20", "green4", "red4"), name = "Construct", guide = 'none') + 
  scale_fill_manual(values = c("grey90", "grey60", "grey60", "grey60", "grey60"), guide = 'none')


#ggsave("boxplots_Hoechst_log.png", width = 10, height = 5)
#ggsave("boxplots_Hoechst_log.svg", width = 10, height = 5)

```


## Check the difference (non-parametric)

```{r}
## subset data
mScdat <- dat[dat$cell.type == "mScarlet", ]
abcb1dat <- dat[dat$cell.type == "abcb1", ]
abcb1mScdat <- dat[dat$cell.type == "abcb1-mScarlet", ]

## why non-parametric: Kolmogorov-Smirnov test with histograms
ks.test(mScdat$RawintDen_H, y = "pnorm")
hist(mScdat$RawintDen_H)
ks.test(log10(mScdat$RawintDen_H+1), y = "pnorm")
hist(log10(mScdat$RawintDen_H+1))
ks.test(mScdat$RawintDen_H, y = "pnorm")
ks.test(abcb1dat$RawintDen_H, y = "pnorm")
ks.test(abcb1mScdat$RawintDen_H, y = "pnorm")

## So, let's just run Dunn's
## mScarlet
dunn.test(x = mScdat$RawintDen_H, g = mScdat$Inhibitor, method = "Holm")

## abcb1
dunn.test(x = abcb1dat$RawintDen_H, g = abcb1dat$Inhibitor, method = "Holm")

## abcb1-mSc
dunn.test(x = abcb1mScdat$RawintDen_H, g = abcb1mScdat$Inhibitor, method = "Holm")
```


## Plot controls only

```{r}

datnoinhib <- dat[dat$`Inhibitor,.type` == "without inhibitor", ]

pcontr <- 
ggplot(datnoinhib, 
       aes(cell.type, log10(RawintDen_H+1))) + 
  geom_boxplot(aes(col = cell.type)) + #geom_jitter(width = .1) +
  geom_signif(comparisons = list(c("mScarlet", "abcb1-mScarlet"), c("mScarlet", "abcb1"), c("abcb1", "abcb1-mScarlet")), 
              map_signif_level = TRUE, step_increase = -.05, test = "wilcox.test", extend_line = 0, margin_top = .1, vjust = .5) + 
  #  geom_hline(yintercept = bkgnd, linetype = "dotted") + 
  ylab("log fluorescence intensity") + 
  xlab("") +
  theme_bw() + theme(axis.text.x = element_text(angle = 90)) + 
  scale_color_manual(values = c("grey20", "green4", "red4"), name = "Construct") + 
  scale_fill_manual(values = c("grey90", "grey60", "grey60", "grey60", "grey60"), guide = 'none')

pcontr

pairwise.wilcox.test(x = datnoinhib$IntDen_H, g = datnoinhib$cell.type)

#ggsave("boxplots_Hoechst_controls.png", width = 5, height = 5)
#ggsave("boxplots_Hoechst_log.svg", width = 5, height = 5)
```

## Plot final multipanel figure

```{r}
figureHoechst <- multi_panel_figure(
  width = 175, height = 175,
  columns = 2, rows = 2)
figureHoechst %<>% fill_panel(pcontr, row = 1, col = 1)
figureHoechst %<>% fill_panel(pall, row = 2, column = 1:2, label = "C")

figureHoechst

#ggsave("Hoechst_both_plots.svg", figureHoechst, width = 180, height = 180, units = 'mm')
#ggsave("Hoechst_both_plots.png", figureHoechst, width = 180, height = 180, units = 'mm')